%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Getsafe} % Organization
    {Berlin, Germany} % Location
    {June 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Senior engineer on Claims team, responsible for insurance claim filing systems and user experience.}
        \item {Develop and maintain service monoliths using Python, FastAPI, Ruby, Rails, PostgreSQL, Elasticsearch, and Kafka.}
        \item {Led integration of generative AI into claims pipeline to streamline filing for customers and managers.}
        \item {Mentor junior engineers and working students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {AutoScout24} % Organization
    {Berlin, Germany} % Location
    {Apr. 2024 - May 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Senior engineer in AutoScout's Listing Intelligence group, where we ingest, enrich and deliver automobile taxonomy data to the whole of AS24.}
        \item {Maintain, build and extend existing microservice architecture using Java, Scala, Spring Boot, WebFlux, and Kafka.}
        \item {Led efforts to promote better engineering practices across teams with the Java Developer Advocate group at AS24.}
        \item {Mentorship of junior engineers on the Listing Intelligence team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Job title
  {AutoScout24 Smyle} % Organization
  {Berlin, Germany} % Location
  {Sept. 2023 - Apr. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Senior engineer on AutoScout Smyle, the first full-service online used car buying service in Germany.}
      \item {Built out backend services for dealer and car stock management using Java, Spring Boot, PostgreSQL, Kafka, and SQS.}
      \item {Led efforts to simplify architecture of stock management system, resulting in overall reduction of incidents and AWS operating costs.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Job title
  {Shopify} % Organization
  {Berlin, Germany} % Location
  {Nov. 2021 - May. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Senior engineer on Shop Minis, a platform enabling 3rd party developers to create native extensions in the Shop marketplace app.}
      \item {Built out back-end infrastructure for APIs using Ruby/Rails/MySQL/GraphQL to allow 3rd party developers to manage and monitor their apps.}
      \item {Led the development of a system to track the total sales of products ordered through 3rd party integrations, allowing merchants to measure the impact of 3rd party integrations.}
      \item {Led the development of tools that allowed for easier onboarding of Merchants to our platform and gave them an overview of it’s impact on their store’s views and sales.}
      \item {Built out analytics dashboards and metrics for both internal monitoring and merchant-facing monitoring using Python, PySpark, Apache Kafka, MySQL, Mode, and React.}
      \item {Direct support of 3rd party developer partners.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Senior Software Architect} % Job title
  {Genedata GmbH} % Organization
  {Munich, Germany} % Location
  {2020 - Nov. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Lead engineer on Genedata Collector, a suite of tools for management, access control and processing of clinical pharmaceutical research data.}
      \item {Led development, design and architecture of the Profiler Data Lake, a tool for advanced object storage, metadata tagging and access control of large data sets using AWS S3, Redshift, and PostgreSQL.}
      \item {Worked with quality assurance management to ensure product suite maintains GxP compliance.}
      \item {Mentorship and management of 2 junior-level engineering reports.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Job title
  {Genedata GmbH} % Organization
  {Munich, Germany} % Location
  {2016 - 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineer on Genedata Profiler, an enterprise patient profiling and data management tool aimed at the biotech and pharma research market.}
      \item {Used technologies such as PostgreSQL, Hibernate, Lucene, Java, and SQL to allow the storage and search of large data sets.}
      \item {Led migration of Oracle/SQL-based codebase to PostgreSQL 9.6/Hibernate, including planning, risk analysis and implementation.}
      \item {Designed a database-driven system for secure storage of patient profiling data.}
      \item {Developed data management and permissions systems using Java, Play, Javascript, and React.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Genedata Inc.} % Organization
{Lexington, Massachusetts, USA} % Location
{2010 - 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Engineer on Genedata Analyst, a highly performant, user-friendly enterprise system for multivariate data analysis and visualization on the web and the desktop.}
    \item {Developed an n-tier application in Java, Swing, and RMI to allow for large-scale data visualization and analysis of data.}
    \item {Implemented web-based management interface using Java, Play, Ember.js, Javascript, and HTML.}
  \end{cvitems}
}

\cventry
{Junior Software Engineer} % Job title
{Genedata Inc.} % Organization
{Lexington, Massachusetts, USA} % Location
{2008 - 2010} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed custom software extensions for large pharmaceutical and bioresearch companies against Genedata Screener public APIs and services.}
  \end{cvitems}
}


%---------------------------------------------------------
\end{cventries}
